Disease and climate effects on individuals drive post-reintroduction

### 2018-11-17 article.Rmd
Optionally include figures at end of article
This will help to make a pdf that works well on biorxiv, and also allow us to generate the pdf that the journal wants (with no embedded figures)

---
title: Disease and climate effects on individuals drive post-reintroduction
  population dynamics of an endangered amphibian
bibliography: library.bib
output:
    pdf_document:
      keep_tex: true
      includes:
          in_header: header.sty
fontsize: 12pt
csl: ecology.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, include = FALSE)
library("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
library(lubridate)
library(tidyverse)
n_digit <- 3
df2num <- function(df, n_digit = 3) {
  stopifnot(nrow(df) == 1)
  stopifnot(ncol(df) == 1)
  df %>%
    unlist %>%
    round(n_digit)
}
```

@@

>>>>

---
title: Disease and climate effects on individuals drive post-reintroduction
  population dynamics of an endangered amphibian
bibliography: library.bib
output:
    pdf_document:
      keep_tex: true
      includes:
          in_header: header.sty
fontsize: 12pt
csl: ecology.csl
params:
  include_figs: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, include = FALSE)

library(knitcitations)
library(lubridate)
library(tidyverse)

cleanbib()
options("citation_format" = "pandoc")
n_digit <- 3
df2num <- function(df, n_digit = 3) {
  stopifnot(nrow(df) == 1)
  stopifnot(ncol(df) == 1)
  df %>%
    unlist %>%
    round(n_digit)
}
```

@@

```{r, echo=FALSE, results='asis', eval=params$include_figs, include=TRUE}
cat("
\\newpage

\\begin{figure}[ht] 
\\caption{}
\\includegraphics[width=\\textwidth]{figure1.pdf}
\\label{hmm-structure} 
\\end{figure}
\\newpage

\\begin{figure}[ht] 
\\caption{}
\\includegraphics[width=\\textwidth]{figure2.pdf}
\\label{detection-effects}
\\end{figure}
\\newpage

\\begin{figure}[ht] 
\\caption{}
\\includegraphics[width=\\textwidth]{figure3.pdf}
\\label{mean-bd-loads}
\\end{figure}
\\newpage

\\begin{figure}[ht] 
\\caption{}
\\includegraphics[width=\\textwidth]{figure4.pdf}
\\label{transition-plot} 
\\end{figure}
\\newpage

\\begin{figure}[ht] 
\\caption{}
\\includegraphics[width=.95\\textwidth]{figure5.pdf}
\\label{abundance-survival-time-series}
\\end{figure}
\\newpage

\\begin{figure}[ht] 
\\caption{}
\\includegraphics[width=\\textwidth]{figure6.pdf}
\\label{bd-load-survival}
\\end{figure}
\\newpage

\\begin{figure}[ht] 
\\caption{}
\\includegraphics[width=\\textwidth]{figure7.pdf}
\\label{introduced-adult-survival}
\\end{figure}
\\newpage

\\begin{figure}[ht]
\\caption{}
\\includegraphics[width=\\textwidth]{figure8.pdf}
\\label{recruitment-time-series}
\\end{figure}
\\newpage
")
```
